|

### 2021-07-30 article/articleCustomerDropoutMembership.Rmd
upd

Other studies proposed also the integration of several algorithms to improve the
performance in the prediction of the dropout such the usage of clusters
combinated with churn prediction [@hung_applying_2006; @gok_case_2015;
@vijaya_sivasankar_2019]. The approach relies in the assumption that combining
the customers in different clusters allows the improvement of the prediction
accuracy. @vijaya_sivasankar_2019 suggested the adoption hybrid models combining
more than one classier are achieving increased performance compared to those
using single classifiers.

@@

```{python pysurvivalperformance, eval=TRUE, echo=FALSE, cache=TRUE, warning = FALSE}
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

@@

The model accuracy is very high in the first years. The prediction is very
similar to the actual value. The absolute error mean of \~37 customers.

@@

estava a aqui a confirmar os clusters, talvez seja melhor reduzir as variáveis...

```{r clusters, echo=FALSE, message=FALSE, warning=FALSE}
library(mclust)
y <- scale(py$df_members)
bic <- mclustBIC(y,modelNames = c("VEI"))
plot(bic)

@@

TODO:

>>>>

Other studies proposed also the integration of several algorithms to improve the
performance in the prediction of the dropout such the usage of clusters
combined with churn prediction [@hung_applying_2006; @gok_case_2015;
@vijaya_sivasankar_2019]. The approach relies in the assumption that combining
the customers in different clusters allows the improvement of the prediction
accuracy. @vijaya_sivasankar_2019 suggested the adoption hybrid models combining
more than one classier are achieving increased performance compared to those
using single classifiers.

@@

```{python pysurvivalperformance, eval=TRUE, echo=FALSE, cache=FALSE, warning = FALSE}
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

@@

The model accuracy is very high in the first years. The prediction is very
similar to the actual value. The absolute error mean of 
`r round(py$results$mean_absolute_error,0)` customers.

@@

Estou a ter problemas com o cálculo dos clusters com o BIC... 
estava a aqui a confirmar os clusters, talvez seja melhor reduzir as variáveis...
testar a abordagem aos clusters no artigo dos vinhos...

```{r clusters, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
library(mclust)
y <- scale(py$df_members)
bic <- mclustBIC(y,modelNames = c("VEI"))
plot(bic)

@@

```{r NbClust, eval=FALSE}
library(NbClust)
nb <- NbClust(y, diss=NULL, distance = "euclidean", 
              min.nc=2, max.nc=5, method = "kmeans", 
              index = "all", alphaBeale = 0.1)
hist(nb$Best.nc[1,], breaks = max(na.omit(nb$Best.nc[1,])))

```

```{python elbowCalculation, eval=TRUE, echo=FALSE, cache=TRUE, warning = FALSE}
from sklearn.cluster import KMeans
from sklearn import preprocessing
from scipy.spatial.distance import cdist
import matplotlib.pyplot as plt

import numpy as np
#Finding optimal no. of clusters
clusters=range(1,20)
meanDistortions=[]

for k in clusters:
    model=KMeans(n_clusters=k)
    model.fit(df_members)
    prediction=model.predict(df_members)
    meanDistortions.append(sum(np.min(cdist(df_members, model.cluster_centers_, 'euclidean'), axis=1)) / df_members.shape[0])

plt.plot(clusters, meanDistortions, 'bx-')
plt.xlabel('k')
plt.ylabel('Average distortion')
plt.show()

```

We are going to consider five clusters

```{python kmeans calculation, eval=TRUE, echo=FALSE, cache=FALSE, warning = FALSE}
cluster = KMeans(n_clusters=5)

cluster.fit(df_members)
df_members['cluster']=cluster.predict(df_members)
print(df_members.cluster.value_counts())
```

```{python kmeans PCA, eval=TRUE, echo=FALSE, cache=FALSE, warning = FALSE}
from sklearn.decomposition import PCA

plt.rcParams['figure.figsize'] = [13, 4]

pca=PCA(n_components=2)
df_members['X_pca']=pca.fit_transform(df_members)[:,0] #todas as linhas da primeira coluna com redução
df_members['Y_pca']=pca.fit_transform(df_members)[:,1] #todas as linhas da segunda coluna com redução

fig, ax = plt.subplots()
for cluster in df_members.cluster.unique():
    x = df_members['X_pca'].loc[df_members.cluster == cluster]
    y = df_members['Y_pca'].loc[df_members.cluster == cluster]
    ax.scatter(x, y, label=cluster, alpha=1, edgecolors='none')

ax.legend()
ax.grid(True)
ax.set_title('Clusters clientes')
```

TODO: fit the model for the five clusters... compare the performance with the model without
clusters... corrigir acima para selecionar só as features

```{python createModelClusters, eval=FALSE, echo=FALSE, cache = TRUE, warning = FALSE}
# Building training and testing sets for the clusters
for cluster in df_members.cluster.unique():
    # Number of samples in the dataset
    df_members_cluster = df_members[df_members.cluster == cluster]
    N = df_members_cluster.shape[0]
    index_train, index_test = train_test_split(range(N), test_size = 0.4)
    data_train = df_members_cluster[features].loc[index_train].reset_index( drop = True )
    data_test  = df_members_cluster[features].loc[index_test].reset_index( drop = True )

    # Creating the X, T and E inputs
    X_train, X_test = df_members_cluster[features], data_test[features]
    T_train, T_test = df_members_cluster[time_column], data_test[time_column]
    E_train, E_test = df_members_cluster[event_column], data_test[event_column]
